Summary of Plasma Diagnostic Methods

### 2021-03-08 paper.tex
Updates from Overleaf

@@

Spectroscopy of radiative plasma self-emission is a

>>>>

Self-emission of bound electrons can be actively stimulated by inducing excitations with electromagnetic radiation at a resonant frequency, generally using a laser. Resonant fluorescence has several advantages over passive spectroscopy. The intensity of line radiation for a particular transition can be increased substantially by tuning the laser frequency, and crossing the viewing and exciting beams can offer a very localized measurement as shown in figure \ref{fig:lif}.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{lif-localized-region.pdf}% Images in 100% size
  \caption{Resonant fluorescence of atomic transitions with orthogonal viewing direction allows a very localized detection region. \citep{Hutchinson_2002}.}
\label{fig:lif}
\end{figure}

@@
